%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 8 February 2019
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,]{moderncv}

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{3873B3}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[scaled=0.86]{DejaVuSansMono}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\def\donothing#1{#1}
\def\emaillink#1{#1}

%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75,footskip=60pt]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...



% personal data
\name{Emma}{Fahey}
\title{Advisor}

 % Phone number
\email{\donothing{\href{mailto:faheyemma@myvuw.ac.nz}{\nolinkurl{faheyemma@myvuw.ac.nz}}}}
 % Personal website



% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted



\quote{Emma is a governmetnal advisor currently completing psyhcology
honours at Victoria Universtiy of Wellington.}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle



\hypertarget{skills}{%
\subsection{Skills}\label{skills}}

\begin{itemize}
\item
  Proficient in R environments ~
\item
  Great Attention to detail ~
\item
  Fast learner\\
\item
  Considerate and understanding\\
\item
  Works well under pressure, independently, and in teams ~
\item
  Resilient ~
\end{itemize}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\nopagebreak
    \cventry{in progress}{Bachelor of Science (honours)}{Psychology}{Victoria University of Wellington}{}{\empty}
    \cventry{2015-2018}{Bachelor of Science}{Ecology, Biodiversity and Psychology}{Wellington, New Zealand}{}{\empty}

\hypertarget{work-history}{%
\subsection{Work History}\label{work-history}}

Advisor - Implementation - \textbf{Ministry of Justice}\\

\emph{October 2019 - Present}

As an Advisor, I have been introduced to the world of implementing
legislation. Scoping, report writing, and project work are just some of
the tasks that I have been privy to in this varied role. During my time
I have learnt about key aspects of the machinery of government and how
the courts interact with the Justice system. I have had the chance to
work on implementing high profile pieces of legislation and enjoyed
working out the politics needed for smooth project delivery.

Team Administrator - \textbf{Ministry of Justice} ~

\emph{April 2019 - October 2019 (fixed term)}

The Team Administrator role operates in a fast-paced working environment
where no two days are the same. Most of the workload is reactive,
meaning I learnt quickly to effectively prioritise work and forecast
upcoming tasks. I found this role rewarding and enjoyed working in a
supportive team environment that values the end user.

Student and whanau support advisor - \textbf{Te Aho o Te Kura Pounamu} ~

\emph{November 2018 - March 2019 (fixed term)}

I worked collaboratively in a team environment to efficiently answer
queries from the public, education community and wider government. This
role regularly involved interpreting policy and translating into clear
and easily understandable way. I also provided both technical and
informative troubleshooting, helping people to see all options that may
be available to them.

\textbf{Working Abroad} ~

\emph{May 2018 -- October 2018}

Traveling and working in Europe. I spent four and a half months
travelling and volunteering on farms, biodynamic community food-share
groups and helping in vineyards and gardening communities. The travel
and exposure greatly opened my mind to different cultures and ways of
life.

Registration officer -- \textbf{Department of Internal Affairs} ~

\emph{November 2016 -- March 2017 (fixed term -- extended)}

The Registration officer role involves registering and dealing with
errors of fact for births, deaths and marriages. I worked in a
tight-knit established team to work towards DIA's goal of bringing all
communities together and had a wide variety of interactions with the
public sector. Key aspects of this role were: customer service, data
entry, logic, high-level decision making, quality assurance, and
managing confidentiality.

\hypertarget{voluntary-work}{%
\subsection{Voluntary Work}\label{voluntary-work}}

Research Assistant - Victoria Universtiy under the instruction of Rachel
Shaw ~

\emph{Late 2016 - 2018}

Helping in the collation of research data during the breeding season of
the North Island Robin at Zealandia wildlife reserve. This included
following the instruction of lead researchers and working together with
them and fellow undergraduates to observe breeding behaviours and find
nests.

Volunteer, archives -- Forest and Bird, Wellington ~

\emph{May to July 2017}

I volunteered in the storeroom, helping to archive and organise old
journal articles and various artefacts for forest and bird for a few
hours every week.


\end{document}

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
