---
title: "Short Article"
description: |
  Article title will go here.
author:
  - name: Emma Fahey
date: "05/23/2021"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


# this code can be used for each chunk where applicable 
# code does or doesn’t display inline (echo setting)
# figures are shown at various sizes (fig.width and fig.height settings)
# warnings and messages are suppressed (warning and message settings)
# computations are cached (cache setting)

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
               echo=TRUE, 
               warning=FALSE, message=FALSE, 
               cache=TRUE)

```

```{r libraries and import, include=FALSE}

### Libraries - delete those uneeded. 
library("tidyverse")
library("patchwork")
library("lubridate")
library("kableExtra")
library("gtsummary")
library("lubridate")
library("equatiomatic")
library("ggdag")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
library("gendercoder")
library("table1")
library("ggplot2")
library("lavaan")

# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())

# read/import data
df <- read_csv("processed_nature.csv") # reading the data. 

df$gender_code <- gendercoder::recode_gender(df$gender) # making the gender codes uniform as were free text entries. 

df <- mutate(df, age_clean = if_else(age < 1000, age, 2021 - age)) # cleaning age variable to remove extreme outliers. 

# first reverse coding items for the happiness scale 

df[,"shs_4"] <- lapply(df[,"shs_4_1" ], function(x){car::recode(x,"1 = 7; 2 = 6; 3 = 5; 4 = 4; 5 = 3; 6 = 2; 7 = 1")})

# scales using: 
# happiness 
# life sat 
# motivations 

# create 3x new columns for motivation variable 
df$motsad <- (df[c("importance_1", "importance_2", "importance_3", "importance_4", "importance_5", "importance_6", "importance_7")])

df$mothap <- (df[c("importance_8", "importance_9", "importance_10", "importance_11")])

df$motref <- (df[c("importance_12", "importance_12", "importance_13", "importance_14")])


# generating mean scores for the scales. # IS THIS ACCURATE??? 
df$motsad <- rowMeans(df[paste0("importance_", 1:7)], na.rm = T)
df$mothap <- rowMeans(df[paste0("importance_", 8:11)], na.rm = T)
df$motref <- rowMeans(df[paste0("importance_", 12:14)], na.rm = T)
df$swls <- rowMeans(df[paste0("swl_", 1:5)], na.rm = T) 
df$shs <- rowMeans(df[paste0("shs_", 1:4, "_1")], na.rm = T) 
mean(df$age_clean)

```

## Introduction 



## Method 

```{r descriptives}

# select the variables needed 
df2 <- df %>%
  select(gender_code, age_clean, swl_1, swl_2, swl_3, swl_4, swl_5, swls, shs_1_1, shs_2_1, shs_3_1, shs_4_1, shs, motsad, mothap, motref)
head(df2)

# table - code for descriptive stats of the scales (means etc.) 
table1::label(df$swls) <- "Life Satisfaction"
table1::label(df$shs) <- "Happiness"
table1::label(df$mothap) <- "Happy Motivation"
table1::label(df$motsad) <- "Sad Motivation"
table1::label(df$motref) <- "Reflective Motivation"

# actual table 
table1::table1(~ swls + shs + mothap + motsad + motref, data = df2)

# histograms 
# desriptive graphs to show distribution of the data 
p1 <-
  qplot(df$swls, geom = "histogram") + labs(title = "Life Satisfaction") + xlab("swls")
p2 <-
  qplot(df$shs, geom = "histogram") + labs(title = "Happiness") + xlab("shs")
p3 <- 
  qplot(df$mothap, geom = "histogram") + labs(title = "Happy Motivation") + xlab("mothap")
p4 <- 
  qplot(df$motsad, geom = "histogram") + labs(title = "Sad Motivation") + xlab("motsad")
p5 <- 
  qplot(df$motref, geom = "histogram") + labs(title = "Reflective Motivation") + xlab("motref")

p1 + p2 + p3 + p4 + p5


# concern is that the 3x IVs are not normally distributed as below... Do I need to adjust the model that I use due to this? 

# Can I do a DAG here or not appropriate? 

```
```{r reliabilities}

print(psych::alpha(df2[paste0("swl_", 1:5)]))
print(psych::alpha(df2[paste0("shs_", 1:4, "_1")]))
print(psych::alpha(df[paste0("importance_", 1:7)]))
print(psych::alpha(df[paste0("importance_", 8:11)]))
print(psych::alpha(df[paste0("importance_", 12:14)]))


# i think there something wrong with the reverse coding of shs.... see reliability output... How do I fix this? 

# other reliability 

print(ufs::scaleStructure(df2[paste0("swl_", 1:5)]))
print(ufs::scaleStructure(df2[paste0("shs_", 1:4, "_1")]))
print(ufs::scaleStructure(df[paste0("importance_", 1:7)]))
print(ufs::scaleStructure(df[paste0("importance_", 8:11)]))
print(ufs::scaleStructure(df[paste0("importance_", 12:14)]))

# reliability graph 

# can't do - error 
# what is EBICglasso, should I be changing this? 


```


```{r basic model code}

# SEM 

mdl_sem <- 'swls ~ motsad + mothap + motref
	shs ~ motsad + mothap + motref'
	
sem_res <- sem(mdl_sem, df2) 
summary(sem_res, standardize = T)

sem_res_strap <- sem(mdl_sem, df, se = "bootstrap") 
summary(sem_res_strap, standardize = T) 

# Bootstrapping randomly grabs part of your data and makes a new average. Allows confidence intervals. 
# IV – 3 diff motivations X
# DV – life sat and happy scores Y

# next steps 
# how do i graph or visually present this? Can I dag it? How do i report it? 
# also what does it all mean? 


```


Text here 



In chunk 2 I think - this code errors. 

network1 <- bootnet::estimateNetwork(select(df2, -age_clean, -gender_code), "EBICglasso")
qgraph::qgraph(network1$graph, layout = "spring")




Other Code we have: 

# Create table data for apa format 
tab_01 = data.frame(
  scale = c("BAS-T", "SR", "BDI", "ASRM", "M-SRM"),
  high = c("46.17 (2.87)", "17.94 (1.88)", "7.11 (6.50)", 
           "6.46 (4.01)", "11.05 (3.36)"),
  moderate = c("37.99 (1.32)", "11.52 (1.84)", "6.18 (6.09)", 
               "5.63 (3.69)", "11.76 (2.75)"),
  p = c("<.001", "<.001", ".254", ".109", ".078")
)

# apa format of a table 
kable(
  tab_01,
  format = "latex",
  booktabs = TRUE,
  escape = FALSE,
  longtable = TRUE,
  col.names = c("Scale", "High BAS group", "Moderate BAS group", "\\textit{p}"),
  align = c("l", "c", "c", "c"),
  caption = "Means and Standard Deviations of Scores on Baseline Measures"
  ) %>%
  row_spec(row = 0, align = "c") %>%
  kable_styling(full_width = TRUE) %>%
  footnote(
    general_title = "Note.",
    general = "Standard deviations are presented in parentheses. BAS = Behavioral Activation System; BAS-T = Behavioral Activation System-Total sores from the Behavioral Inhibition System/Behavioral Activation System Scales; SR = Sensitivity to Reward scores from the Sensitivity to Punishment and Sensitivity to Reward Questionnaire; BDI = Beck Depression Inventory scores; ASRM = Altman Self-Rating Mania Scale scores; M-SRM = Modified Social Rhythm Metric Regularity scores.",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE
    )



