---
title: "What Makes a Place Meaningful?"
description: |
  The Potential Predicitve Power of Meaningful Places on Subjective Wellbeing.
author:
  - name: Emma Fahey
date: "06/04/2021"
output:
  distill::distill_article:
    self_contained: false
bibliography: [r-references.bib]
---

```{r setup, include=FALSE}

# this code can be used for each chunk where applicable 
# code does or doesn’t display inline (echo setting)
# figures are shown at various sizes (fig.width and fig.height settings)
# warnings and messages are suppressed (warning and message settings)
# computations are cached (cache setting)

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
               echo=TRUE, 
               warning=FALSE, message=FALSE, 
               cache=TRUE)

```

```{r libraries and import, include=FALSE}

#Libraries  
library(gendercoder)
library(rstan)
library(readr)
library(dplyr)
library(table1)

# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())

# read/import data
df <- read_csv("processed_nature.csv") # reading the data. 

df$gender_code <- gendercoder::recode_gender(df$gender) # making the gender codes uniform as were free text entries. 

df <- mutate(df, age_clean = if_else(age < 1000, age, 2021 - age)) # cleaning age variable to remove extreme outliers. 

# reverse coding an item from the happiness scale 
df[,"shs_4_1"] <- lapply(df[,"shs_4_1" ], function(x){car::recode(x,"1 = 7; 2 = 6; 3 = 5; 4 = 4; 5 = 3; 6 = 2; 7 = 1")})

# create 3x new columns for motivation variable (as scale split in 3)
df$motsad <- (df[c("importance_1", "importance_2", "importance_3", "importance_4", "importance_5", "importance_6", "importance_7")])

df$mothap <- (df[c("importance_8", "importance_9", "importance_10", "importance_11")])

df$motref <- (df[c("importance_12", "importance_12", "importance_13", "importance_14")])

# generating mean scores for the scales. 
df$motsad <- rowMeans(df[paste0("importance_", 1:7)], na.rm = T)
df$mothap <- rowMeans(df[paste0("importance_", 8:11)], na.rm = T)
df$motref <- rowMeans(df[paste0("importance_", 12:14)], na.rm = T)
df$swls <- rowMeans(df[paste0("swl_", 1:5)], na.rm = T) 
df$shs <- rowMeans(df[paste0("shs_", 1:4, "_1")], na.rm = T) 

mean(df$age_clean, na.rm = T)

```

## Introduction

If I were to tell you to think of a meaningful place right now, would one come to mind? In most cases, the answer to this question would be yes. It is believed that we have an innate connection to certain places, this is defined as topophilia and has been studied for many years [@tuan1990]. Places, particularly natural ones, are known to have restorative psychological effects when visited [@ratcliffe2018; @scannell2017; @ulrich1981]. It is thought that people imbue environments with meaning arising from their current needs and wellbeing [@kerr1999]. Favourite or meaningful places have been studied as a way of environmental self-regulation, a coping mechanism to enhance subjective wellbeing and promote emotional regulation [@korpela1992; @korpela2010].

These ideas have been taken a step further by looking at illicit emotional responses in the brain in reaction to meaningful places, providing evidence that meaningful places are unique as our brains process images of them differently to other places [@gatersleben2020; @lengen2012]. With places becoming restricted or forbidden during COVID-19, it is an important time to measure how our use of meaningful places might be affecting our wellbeing. Findings of quality of life decreasing during COVID-19 if no emotion regulation was occurring [@panayiotou2021] furthers this point. Emotion dysregulation has also been found to predict greater acute COVID-19 stress and is a vulnerability factor to poor stress responses [@tyra2021].

Life satisfaction and happiness are frequently studied together worldwide. The two terms have been used under the heading of subjective wellbeing [@selim2008] and hedonic wellbeing [@difabio2015; @kahneman1999]. Studies include measures of cultural variation, [@bastian2014] in relation to suicide rates [@bray2006], in relation to physical health in elderly populations [@lara2020], in relation to wellbeing trends as populations age [@an2020], and more recently in response to the COVID-19 pandemic [@bozkurt2021]. Happiness in particular is rated as an important characteristic for subjective wellbeing, with college students in one study rating it on average 8.1 out of 9 for importance, compared to other wellbeing characteristics [@kim-prieto2005].

The current study looks at life satisfaction and happiness scores in relation to the importance or motivation to visit a meaningful place. Importance is split up into three subcategories: happy, sad, and reflective reasons to visit a place. The question is if motivations to visit a meaningful place predict subjective wellbeing. Hypotheses include (1) the motivation to visit a meaningful place in a positive mood will relate to higher subjective wellbeing scores. Conversely, the motivation to visit for a negative reason will relate to lower overall subjective wellbeing. (2) Consistent with @korpela2020, life satisfaction will be positively associated with sad and happy motivations to visit a place, but not reflective motivations.

## Method

**Participants** (*n* = 303) were recruited through an undergraduate introduction to psychology course at Victoria University, Wellington, New Zealand. Participants were awarded course credit for taking part in the study. The mean age of participants was 19.45 (SD = 4.46) with an age range of 17-69. One outlier was removed from the data set for having an age over 1000. 80.8% of participants identified as female (*n* = 245), 15.5% male (*n* = 47), and 3.1% non-binary (*n* = 3). 8 participants did not supply a gender identification.

**Procedure.** Participants took part in the survey online through Qualtrics. The survey was broken into two sections. Part one contained the upload of a meaningful image to the participant. This was followed by open-field questions to determine the meaning of the place and two scales to determine the places importance and situational meaning. The second part of the survey included self-measures for nature connectedness and a variety of wellbeing measures. The survey took approximately 30 minutes to complete, and participants could withdraw at any time. Only the three scales described below will be used in the current report. For our analysis we used `r papaja::cite_r("r-references.bib", footnote = T)`

### Materials

**Happiness** was measured by the measure of subjective happiness scale [@lyubomirsky1999]. This scale consists of 4 items that are rated between 1 and 7. Values of the scale differed for each question. The following statement was provided before commencement "For each of the following statements and/or questions, please select the point on the scale that you feel is most appropriate in describing you." A mean happiness score for each participant was calculated by summing all items. The full scale can be found in the appendix \@ref(shs)

**Life Satisfaction** was assessed using the Satisfaction with Life Scale (SWLS) [@diener1985]. Participants responded to a likert 7-point scale. The items were preceded by the statement: "Below are five statements that you may agree or disagree with. Using the 1 -- 7 scale below indicate your agreement with each item. Please be open and honest in your responding." The scale ranged from 1(strongly disagree) to 7(strongly agree). A mean life satisfaction score for each participant was created by summing all items. The full scale can be found in the appendix \@ref(swls)

**Motivations to visit a place.** An amended version of the importance of places scale [@korpela2020] was administered to participants to assess the reasons that place was visited. Participants responded on a likert 7-point scale which ranged from 1 (not at all) to 7 (very important). Due to initial confirmatory factor analysis results from @korpela2020, we amended the scale from 19 items down to 13. We then added the item "when wanting to meditate" to the alone or reflective category. The final 14-item scale was prefaced with the statement: "How important are the following situations as reasons to visit the place in the photo?" These reasons create three subfactors: Happy or well (4-items), alone or reflective (3-items), and sad or depressed (7-items) motivations. Items were grouped into the above categories and a sum score was calculated for each category. The full scale can be found in the appendix \@ref(mot)

**Scale Statistics**

The spread of responses to each scale are shown in fig \@ref(fig:plots). This allows us to check if scale distribution is normal to fit the assumptions of the structural equation model.  

```{r descriptives, include=FALSE}

# select the variables needed 
df2 <- df %>%
  select(gender_code, age_clean, swl_1, swl_2, swl_3, swl_4, swl_5, swls, shs_1_1, shs_2_1, shs_3_1, shs_4_1, shs, motsad, mothap, motref)
head(df2) # checking the variables 

# table - code for descriptive stats of the scales (means etc.) 
table1::label(df$swls) <- "Life Satisfaction"
table1::label(df$shs) <- "Happiness"
table1::label(df$mothap) <- "Happy Motivation"
table1::label(df$motsad) <- "Sad Motivation"
table1::label(df$motref) <- "Reflective Motivation"

# actual table 
table1::table1(~ swls + shs + mothap + motsad + motref, data = df2)

# histograms - desriptive graphs to show distribution of the data 
p1 <-
  qplot(df$swls, geom = "histogram") + labs(title = "Life Satisfaction") + xlab("swls")
p2 <-
  qplot(df$shs, geom = "histogram") + labs(title = "Happiness") + xlab("shs")
p3 <- 
  qplot(df$mothap, geom = "histogram") + labs(title = "Happy Motivation") + xlab("mothap")
p4 <- 
  qplot(df$motsad, geom = "histogram") + labs(title = "Sad Motivation") + xlab("motsad")
p5 <- 
  qplot(df$motref, geom = "histogram") + labs(title = "Reflective Motivation") + xlab("motref")

```

```{r plots, echo=FALSE, fig.cap= "Distribution of scales in present study"}
plot(p1 + p2 + p3 + p4 + p5)
```

```{r reliabilities, include=FALSE}

# alpha reliability calculation 
print(psych::alpha(df2[paste0("swl_", 1:5)]))
print(psych::alpha(df2[paste0("shs_", 1:4, "_1")]))
print(psych::alpha(df[paste0("importance_", 1:7)]))
print(psych::alpha(df[paste0("importance_", 8:11)]))
print(psych::alpha(df[paste0("importance_", 12:14)]))

# other reliability calculation 
print(ufs::scaleStructure(df2[paste0("swl_", 1:5)]))
print(ufs::scaleStructure(df2[paste0("shs_", 1:4, "_1")]))
print(ufs::scaleStructure(df[paste0("importance_", 1:7)]))
print(ufs::scaleStructure(df[paste0("importance_", 8:11)]))
print(ufs::scaleStructure(df[paste0("importance_", 12:14)]))

# these have been added to the apa format table in the code chunk below. 

```

The main descriptive statistics for each scale can be found in table 1. Multiple reliability tests were run to determine the scales alpha, omega and coefficient H. This is because the alpha reliability alone assumes scales are uni-dimensional and normally distributed. Items in each motivations to visit a place subscale were not shown to be normally distributed in fig \@ref(fig:plots) above.  

**Table 1**

```{r, echo=FALSE, results='asis'}

# Create table data for apa format 

tab_01 = data.frame(
  scale = c("SHS", "SWLS", "MotHap", "MotSad", "MotRef"),
  Mean = c("4.27 (0.76)", "4.49 (1.27)", "5.13 (1.56)", 
           "4.04 (1.69)", "4.73 (1.82)"),
  Alpha = c("0.87", "0.84", "0.90", "0.94", "0.82"),
  Omega = c("0.89", "0.88", "0.92", "0.96", "0.83"), 
  Coefficient_H = c("0.88", "0.87", "0.94", "0.95", "0.85")
)

library(kableExtra)

# apa format of a table 

kable(
  tab_01,
  format = "html",
  booktabs = TRUE,
  escape = FALSE,
  longtable = TRUE,
  col.names = c("Scale", "Mean(SD)", "Alpha", "Omega", "Coefficient_H"),
  align = c("l", "c", "c", "c", "c"),
  caption = "Descriptive statistics and reliabilities of present study scales, N = 302"
  ) %>%
  row_spec(row = 0, align = "c") %>%
  kable_styling(full_width = TRUE) %>%
  footnote(
    general_title = "Note.",
    general = "SHS = Subjective Happiness Scale; SWLS = Satisfaction with Life Sacle; MotHap = Happy Motivation Subscale; MotSad = Sad Motivation Subscale; Motref = Refletive Motivation Subscale.",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE
    )

```

The initial use of the motivations to visit a place scale had comparable reliability, with cronbach's alpha being reported as 0.93 for sad motivation, 0.87 for happy motivation and 0.8 for alone motivation subscales [@korpela2020].  

### Networks

A network graph, shown in fig \@ref(fig:net1) is used to display the connectedness of the scales used in the current study. As expected, life satisfaction and happiness form a connection. The three subscales of motivations to visit a place form a strong connection.  

```{r net1, echo=FALSE, fig.cap= "Network graph of the current studies scales"}
# creating a network map of scale items 
network1 <- bootnet::estimateNetwork(select(df2, -age_clean, -gender_code, -shs, -swls), "EBICglasso")
owl <- qgraph::qgraph(network1$graph, layout = "spring")
# the above shows that happiness and life satisfaction form a connection. 

```

The exploratory graph analysis (EGA) in fig \@ref(fig:networks) shows that life satisfaction and happiness are still separate constructs, but that the three subscales of motivations to visit a place may be measuring only one construct. To ensure the new motivations to visit a place subscales were measuring three separate constructs, a second exploratory graph analysis was run (see appendix \@ref(fig:appen1)). This shows that the subscales are connected, yet independent constructs. A network graph was also run for the new subscales to ensure that items selected to mean happy, sad, and reflective are most connected to those selected constructs. This was found to be accurate (see appendix \@ref(fig:appen2)).

```{r networks, echo=FALSE, fig.cap= "EGA graph of current studies scales showing three seperate constructs"}

ega <- EGAnet::bootEGA(select(df2, -age_clean, -gender_code, -shs, -swls), layout = "spring", iter = 1000)

# the above shows us that life satisfaction and happiness are independent constructs. 

```

### Correlation Analysis

Fig \@ref(fig:corr) depicts correlations between scales. All correlations are run with Holm adjustment, this reduces the possiblilty of a statistically significant result, or type 1 error when performing multiple tests. This correction is more statistically powerful than a Bonferroni adjustment

(ADD CITE ONCE SYNCHED).

Life satisfaction and happiness correlate significantly. All three motivations for visiting a place correlate significantly, with reflective and sad being the strongest. These results are comparable with those of @korpela2020 that found sad and reflective to correlate at 0.68, sad and happy to correlate at 0.32, and reflective and happy to correlate 0.35.

```{r corr, echo=FALSE, fig.cap= "Correlation plot of scales in current study"}

ggstatsplot::ggcorrmat(df, c("age_clean", "swls", "shs", "motsad", "mothap", "motref"), 
                       cor.vars.names = c("age", "Life Satisfaction", "Happiness", "Sad Motivation", "Happy Motivation", "Reflective Motivation"))

```

### Model Selection

```{r semresmodelcode, include=FALSE}

library(lavaan)

# SEM to test hypoth

mdl_sem <- 'swls ~ motsad + mothap + motref
	shs ~ motsad + mothap + motref' # this is the model 

sem_res_strap <- sem(mdl_sem, df2, se = "bootstrap", estimator = "ML")  # this is running a bootstrap version of the above model. 

```

```{r modsel, echo=FALSE, fig.cap= "Conceptual structural equation model of the present study. mts = sad motivation subscale; mth = happy motivation subscale; mtr = reflective motivation subscale; swl = satisfaction with life scale; shs = subjective happiness scale"}

# path model of the equation
semPaths(sem_res_strap, layout = "tree") 

```

A structural equation model (SEM) (fig \@ref(fig:modsel)) is run in this study to analyse motivations to visit a meaningful place against life satisfaction and happiness. The maximum likelihood estimation (ML) is employed, which presumes multivariate normality of the variables. As stated previously, and depicted in fig \@ref(fig:plots), the motivations to visit a place subscales were not normally distributed, so a bootstrap adjustment was fitted to the model. This runs the same analysis 1,000 times to get an average which creates more reliable and robust results, particularly when considering non-normality. 

## Results

The structural equation model (SEM) is fully saturated (CFI = 1). Therefore, a second model to determine if model fit differs by gender is run. Regression paths are identical between groups (CFI = 1 for both), which implies that gender does not impact the model. This allows the model to be confidently collapsed together.

The main model is depicted in table 2 and shows that only happy motivations to visit and happiness scores were significant (B = 0.139, *p*=0.010). However, happy motivation and life satisfaction scores were near significance (B = 0.104, *p*=0.070), this is likely due to the correlation between happiness and life satisfaction. Reflective motivations to visit a place on subjective wellbeing were non-significant but positive (B = 0.033 - 0.043), whereas sad motivations for visiting a meaningful place on subjective wellbeing were non-significant and negative (B = -0.065 - -0.067). A model depiction of the results can be found in appendix \@ref(fig:resdep).

```{r basic model code, include=FALSE}

# first run of the SEM model
summary(sem_res_strap, standardize = T, fit = T) #this reports the model in a readable format 

# second run of SEM model to see if the model differs per gender. 
	
sem_res_1 <- sem(mdl_sem, filter(df2, gender_code %in% c("male", "female")), estimator = "ML", group = "gender_code", se = "bootstrap") 
sem_res_mtr <- sem(mdl_sem, filter(df2, gender_code %in% c("male", "female")), estimator = "ML", group = "gender_code", group.equal = "regressions", se = "bootstrap")
# MLR uses approx to multuvariate data and using scaling factor to adjust qui-squared. Like a students t-test. But instead we using ML (the norm), and bootstrap. This runs the analysis 1000 times to get an average answer. 


summary(sem_res_1, standardize = T, fit = T) 
summary(sem_res_mtr, standardize = T, fit = T)
# once generated these, we looking at the cfi - the differences. 

# Bootstrapping randomly grabs part of your data and makes a new average. Allows confidence intervals. 

# from this 2x sig (mothap and shs in both). 


```

```{r rtab, echo=FALSE}

parameterestimates(sem_res_strap) %>%
  filter(., op == "~") %>%
  mutate(B = paste0(round(est,3), "[", round(ci.lower, 3), ", ", round(ci.upper, 3), "]")) %>%
  select(., lhs, rhs, B, pvalue) %>%
  rename(., Outcome = lhs, Predictor = rhs, p = pvalue) %>%
  papaja::apa_table(.,
                    caption = "Structural equation model results, N = 302",
                    note = "swls = life satisfaction scale; shs = happiness scale; motsad = sad motivation subscale; mothap = happy motivation subscale; motref = reflective motivation subscale")

```

## Discussion

The aim of the current study was to see if motivations to visit a meaningful place could predict subjective wellbeing. I found partial support for the first hypothesis, that the motivation to visit a meaningful place in a positive mood does relate to higher subjective wellbeing scores. This was supported by positive and statistically significant paths between subjective happiness scores and happy motivations to visit a meaningful place. There was also some support for the converse of this, with sad motivations to visit a meaningful place having negative paths to both subjective wellbeing measures, however these were not significant.

Support was not found for hypothesis two, as life satisfaction was positively associated with happy and reflective reasons, and negatively with sad reasons. None of these paths were significant. This does not support @korpela2020 study.

**Implications**

Findings from the current study can be extrapolated to wider research in emotion regulation and place attachment.... Inferences can be made that it seems to be about knowing what makes you happy, or going to meaningful place for a happy reason, not a sad or reflective one that has an impact on your subjective wellbeing.

This does support the notion that we have an attachment to places and that they can influence our wellbeing, which supports the topophilia hypothesis (CITE).

**Limitations and Future Research**

This research is reliant on participants identification of a meaningful place. As a university sample was used to collect data, there is a fear that answers may not have been accurate, and that there may have been participant response bias (CITE).   ALSO SELF REPORT BIAS.

A study of 17-to-25 year olds found that wellbeing varies significantly with age and gender @lópez-madrigal2021. This may create another limitation of the current study, particularly as the SEM was run on different genders.  

Finally, the current study includes a scale that has not been widely tested on different populations and age groups. It was initially created for the public of Finland and Hungary and has now been tested on an undergraduate population of New Zealand. The results of this study do not reflect wider cultural or age demographics and should be interpreted with caution if generalising across these areas.   

Future research could test the scale with different populations and age ranges to improve its scope and generalisability. The ideas of meaningful places should also be tested more empirically (rather than self-report scales) in the future, with open text data or neuroimaging when visiting meaningful places, or stress responses for example. Further quantification of meaningful places and what they mean to and for us and measuring more than one place and more than two levels of subjective wellbeing should also be explored.

## Appendix

Items are grouped into the following three categories and then sum scored within their category. Happy or well (items 8-11), Alone or reflective (items 12-14), Sad or depressed (items 1-7).

The exploratory graph analysis (EGA) in appendix \@ref(fig:appen1) presents items from the motivations to visit a place scale as three separate constructs.

```{r appen1, echo=FALSE, fig.cap= "EGA of itema in motivations to visit place subscales in the current study showing three seperate constructs."}

library(dplyr)

df10 <- df %>%
  select(age_clean, gender_code, importance_1, importance_2, importance_3, importance_4, importance_5, importance_6, importance_7, importance_8, importance_9, importance_10, importance_11, importance_12, importance_13, importance_14, motsad, mothap, motref)

ega3 <- EGAnet::bootEGA(select(df10, -age_clean, -gender_code, -motsad, -mothap, -motref), iter = 1000)
# the above shows us that there are 3 clear independent constructs for motivation.  

```

The network distribution graph in appendix \@ref(fig:appen2) shows the item correlations of the reasons to visit a place scale. The purpose of this was to see if there were three main groups found to allow for three sub-scales to be created.

```{r appen2, echo=FALSE, fig.cap= "Network Graph of items in the motivations to visit places subscales in the current study"}

# creating a network map of scale items 
network3 <- bootnet::estimateNetwork(select(df10, -age_clean, -gender_code, -motsad, -mothap, -motref), "EBICglasso")
owl <- qgraph::qgraph(network3$graph, layout = "spring")
 

```

The results to the structural equation path mode are also depicted in fig \@ref(fig:resdep).

```{r resdep, echo=FALSE, fig.cap= "Structural equation path model of current study. Note. positive paths are green, negative are red. All values reported are the unstandardised beta. The only paths with significance in this model are between swl and shs and shs and mothap."}

# add to results - to interpret!! 
semPlot::semPaths(sem_res_strap, "est",
                  layout = "spring",
                  exoVar = FALSE,
                  exoCov = FALSE,
                  sizeMan = 15, sizeInt = 15, sizeLat = 15,
                  edge.label.cex=1.5,
                  fade=FALSE)

# std is standard estimates, can also use "par" which would report unstandardised estimates 
# can see that positively are mothap and motref, but neg is motsad, that's good!!!

# the findigs are shown in the below correlation plot. # unsure if needed, Maybe in appendix. 
# semPlot::semCors(sem_res_strap, include = "observed")


# DO A TABLE INSTEAD - TO REPORT all the estimates and p-values. 

papaja::r_refs("r-references.bib")

```

### **Subjective Happiness Scale** {#shs}

For each of the following statements and/or questions, please select the point on the scale that you feel is most appropriate in describing you.

1.  In general, I consider myself: 1 (not a very happy person) to 7 (a very happy person)
2.  Compared with most of my peers, I consider myself: 1 (less happy) to 7 (more happy)
3.  Some people are generally very happy. They enjoy life regardless of what is going on, getting the most out of everything. To what extent does this characterization describe you? 1 (not at all) to 7 (a great deal)
4.  Some people are generally not very happy. Although they are not depressed, they never seem as happy as they might be. To what extent does this characterization describe you? 1 (not at all) to 7 (a great deal)

### **Satisfaction with Life Scale** {#swls}

Below are five statements that you may agree or disagree with. Using the 1 -- 7 scale below indicate your agreement with each item. Please be open and honest in your responding. 

Scale from 1 (strongly disagree) to 7 (strongly agree).

1.  In most ways my life is close to ideal.
2.  The conditions of my life are excellent.
3.  I am satisfied with my life.
4.  So far I have gotten the important things I want in life.
5.  If I could live my life over, I would change almost nothing.

### **Motivations to visit a place scale** {#mot}

How important are the following situations as reasons to visit the place in the photo? (Rating scale from 1 (not at all) to 7 (very important))

1.  When sad
2.  When depressed
3.  Someone has left/rejected me
4.  After having an argument with someone
5.  Having had setbacks
6.  When insecure about myself
7.  When angry
8.  When happy
9.  When everything is going well
10. When in a good mood
11. When feeling powerful
12. When wanting to be alone
13. When wanting to reflect
14. When wanting to meditate
