---
title: "An Example of a Varying Slope Model"
description: |
  Workbook 10 for the fulfillment of 447 course (VUW).
author:
  - name: Emma Fahey
date: 05-12-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r code, include=FALSE}
# libraries 
library(dplyr)
library(lubridate)


# read data

nz_0 <- as.data.frame(readr::read_csv2(
  url(
    "https://raw.githubusercontent.com/go-bayes/psych-447/main/data/nzj.csv"
  )
))

# to re-level kessler 6 variables
f <-
  c(
    "None Of The Time",
    "A Little Of The Time",
    "Some Of The Time",
    "Most Of The Time",
    "All Of The Time"
  )

# get data into shape
nz_cr <- nz_0 %>%
  dplyr::mutate_if(is.character, factor) %>%
  dplyr::select(
    -c(
      SWB.Kessler01,
      SWB.Kessler02,
      SWB.Kessler03,
      SWB.Kessler04,
      SWB.Kessler05,
      SWB.Kessler06
    )
  ) %>% 
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(FeelHopeless = forcats::fct_relevel(FeelHopeless, f)) %>%
  dplyr::mutate(FeelDepressed = forcats::fct_relevel(FeelDepressed, f)) %>%
  dplyr::mutate(FeelRestless = forcats::fct_relevel(FeelRestless, f)) %>%
  dplyr::mutate(EverythingIsEffort = forcats::fct_relevel(EverythingIsEffort, f)) %>%
  dplyr::mutate(FeelWorthless = forcats::fct_relevel(FeelWorthless, f)) %>%
  dplyr::mutate(FeelNervous = forcats::fct_relevel(FeelNervous, f)) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(male_id = as.factor(Male)) %>%
  dplyr::mutate(date = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  dplyr::mutate(
    FeelWorthless_int = as.integer(FeelWorthless),
    FeelNervous_int =  as.integer(FeelNervous),
    FeelHopeless_int =  as.integer(FeelHopeless),
    EverythingIsEffort_int =  as.integer(EverythingIsEffort),
    FeelRestless_int =  as.integer(FeelRestless),
    FeelDepressed_int =  as.integer(FeelDepressed),
    HLTH.Fatigue_int = as.integer(HLTH.Fatigue + 1)
  ) %>%
  dplyr::mutate(yearS = TSCORE - min(TSCORE, na.rm = TRUE)) %>%
  dplyr::mutate(KESSLER6sum = as.integer(KESSLER6sum))

## if you do anything with covid (warning, such a model would be tricky)

ord_dates_class <- c("Baseline",
                     "PreCOVID",
                     "JanFeb",
                     "EarlyMarch",
                     "Lockdown",
                     "PostLockdown")

nzl <- nz_cr %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::mutate(yearS = (TSCORE - min(TSCORE)/365)) %>%
  dplyr::mutate(WSCORE = as.factor(WSCORE)) %>%
  dplyr::mutate(Covid_Timeline =
                  as.factor(ifelse(
                    TSCORE %in% 3896:3921,
                    # feb 29 - march 25th
                    "EarlyMarch",
                    ifelse(
                      TSCORE %in% 3922:3954,
                      "Lockdown",
                      #march 26- Mon 27 April 2020
                      ifelse(
                        TSCORE > 3954,
                        # after april 27th 20202
                        "PostLockdown",
                        ifelse(
                          TSCORE %in% 3842:3895,
                          # jan 6 to feb 28
                          "JanFeb",
                          ifelse(TSCORE %in% 3665:3841 &
                                   Wave == 2019,
                                 "PreCOVID",
                                 "Baseline"  # 3672 TSCORE or  20 July 2019))))))))
                          )
                        )
                      )
                    ))))%>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class))

library("tidyverse")
library("patchwork")
library("lubridate")
library("kableExtra")
library("gtsummary")
library("lubridate")
library("ggdag")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")

```

## Week 10 Workbook 

1. Using the nzl dataset or another dataset of your choice, write a varying intercept/varying slope model.

The variables I have identified to answer this question are Personal Relationships and Agreeableness. This is due to the potential association between the variables over the years (waves). I hypothesize that as agreeableness increase, personal relationships should also increase. I expect these variables to change slightly over years as people develop and grow. 

### Brief Methods 
The data for this short report is taken from the New Zealand Attitudes and Values over time dataset (NZAVS). This dataset includes 2845 individuals that have responded on at least five different years to both personal relationship and agreeableness questions. 

We fit the variables to a varying slope model to try and determine if the relationship between agreeableness and personal relationships changes over time. Each slope represents a different wave of the data (or different year that data was collected). 

Finally, we fit the model to a conditional effects graph to check that the two variables do indeed associate with each other in some way. 


```{r, question, include=FALSE}

# first need to select variables 
nz5 <- nz_cr %>% 
  select(Wave, Your.Personal.Relationships, AGREEABLENESS)

# x ~ 1 + y + (1 + y | category)
# x - Agreeable  
# y - your personal relationships 
# category - Wave

# varying slope code 
vslope2 <-
  brm(
    AGREEABLENESS ~ 1 + Your.Personal.Relationships + (1 + Your.Personal.Relationships | Wave),
    file = here::here("models", "multi-var-slopes"),
    data = nz5,
    family = gaussian
  )

# print the output 
options(width = 120)
summary(vslope2, prior = TRUE)


```

```{r code to include 1}

# create a table of the output to understand 
sjPlot::tab_model(vslope2)

# create a graph of the output 
p2 <- brms::mcmc_plot(vslope2, 
               type = "areas",
               prob = .89)
p2

```


The above model does not appear to fit the model perfectly, so we then attempted to remove the random slope to see if we could generate a model that fits data better. The below model and graph is the result: 


```{r, take 2, include=FALSE}

# removing the random slope to see if the model will fit better. 

vslope3 <-
  brm(
    AGREEABLENESS ~ 1 + Your.Personal.Relationships + (1 | Wave),
    file = here::here("models", "multi-var-slope3"),
    data = nz5,
    family = gaussian
  )

 
# print the output 
options(width = 120)
summary(vslope3, prior = TRUE)


```

```{r code to include 2}

# create a table of the output to understand 
sjPlot::tab_model(vslope3)

# create a graph of the output 
p3 <- brms::mcmc_plot(vslope3, 
               type = "areas",
               prob = .89)
p3

#this second model fits slightly better on graph, but is still difficult to interpret. 

conditional_effects(vslope3) # conditional effects graph 

```



### Discussion 

Both models above do not appear to fit the data particularly well and we can interpret that the models explanatory power is weak (R2 = 0.02, 89% CI [0.02, 0.03], adj. R2 = 0.02).

From the conditional effects graph above, however, we can see that there may be a relationship between the two variables as this graph shows that as personal relationships increase, so do does agreeableness ratings or scores. Perhaps this relationship is simply consistent over time, which is why no large difference was found over the years in the varying slope models. 

The other limitation of the models fit could be due to the dataset containing the same individuals over several years. Perhaps with different populations, ethnicities and/or countries measures there may be a more varying degree in the way these two variables associate. 
