---
title: "welcome"
description: |
  A short description of the post.
author:
  - name: Unknown
date: 05-12-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r code}

```

## Week 10 Workbook 

1. Using the nzl dataset or another dataset of your choice, write a varying intercept/varying slope model.

Johannes outline: 
depression x productivity - slope model. But diff places have diff levels of productivity (varying intercepts). Baseline level differs over diff countries. 

Can also have varying slopes, relationship between productivity and depression differ across diff countries. 

Better estimation with multiple lines than just fitting one line. 

Fit the nz1 - each 5 waves (so should have 5 lines). 

```{r, question}



```

Note the nzl dataset now includes 2845 individuals who have responded to at least five waves of the NZAVS. The dataset now includes relationship satisfaction Your.Personal.Relationships and employment security Emp.JobSecure


Add to the bio: 
# Let's do some mind thinking 
# if in doubt message someone